---
title: "Big_map"
output: html_document
date: '2022-08-18'
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE) 

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library("reshape")
library(ggplot2)
library(ggpubr)
theme_set(theme_pubr())
library(stringr)
library(patchwork)
```

In this markdown I would like to run my newts and snake simulation on a larger map. The prediction that is when I create a larger map there will be more opportunities for different areas to co-evolve, creating a mosaic pattern. The BIG map to be 100 times larger than the long map. The demotions would be; length=1,400 width=350. This would increase the amount of individuals and grid data-points in my simulations. 

In my current simulations, there are about 6,000 individuals (combination of newts and snakes). If I increase the map's area by 100 I expect that the number of individuals would also increase by 100 (~600,000). To make these simulations work/run faster I will increase the starting population size to 2,500 per each species. I also plan on taking information from the simulations less often (e.g. taking information every 50 generations instead of 20) and for a shorter amount of time (e.g. from 50,000 generation to only 10,000 generations). 

My previous simulations ran for 50,000 generations and took a day or less to run (msprime+slim). I will make some plots to see how long these larger simulations will take to run  


```{bash, data file gathering}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=big_map
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA20050_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA20050_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA20050_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")



#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt



for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA20050_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```

```{bash, data file gathering longer run}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=big_map_30
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA20050_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA20050_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA20050_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")



#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt



for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA20050_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```


```{r, data gathering}

snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)

big_map_tall<- read.csv("~/Desktop/big_map/all_lit.txt" , header = TRUE)
filter_col=grepl( "X" , names( big_map_tall ))
big_map_tall= big_map_tall[, filter_col==FALSE]
big_map_tall_30<- read.csv("~/Desktop/big_map_30/all_lit.txt" , header = TRUE)
big_map_tall_30$rep=1
big_map_tall<-rbind(big_map_tall, big_map_tall_30)

big_map_tall$group_rep <- paste0(big_map_tall$snake_mu_rate, "_", big_map_tall$snake_mu_effect_sd,"_",big_map_tall$newt_mu_rate, "_", big_map_tall$newt_mu_effect_sd, "_", big_map_tall$rep)

big_map_tall$group <- paste0(big_map_tall$snake_mu_rate, "_", big_map_tall$snake_mu_effect_sd,"_",big_map_tall$newt_mu_rate, "_", big_map_tall$newt_mu_effect_sd)

big_map_tall$sim=LETTERS[factor(big_map_tall$group)]
big_map_tall$dif <- big_map_tall$Snake_mean_Pheno-big_map_tall$Newt_mean_Pheno
big_map_tall$snake_newt_rep <- paste0("Snake_",big_map_tall$snake_mu_rate, "_", big_map_tall$snake_mu_effect_sd, "_Newt_",big_map_tall$newt_mu_rate, "_", big_map_tall$newt_mu_effect_sd, "_", big_map_tall$rep)



big_map_cor<- read.csv("~/Desktop/big_map/all_cor.txt" , header = TRUE)
filter_col=grepl( "X" , names( big_map_cor ))
big_map_cor= big_map_cor[, filter_col==FALSE]
big_map_cor_30<- read.csv("~/Desktop/big_map_30/all_cor.txt" , header = TRUE)
big_map_cor_30$rep=1
big_map_cor<-rbind(big_map_cor, big_map_cor_30)
big_map_cor$group_rep <- paste0(big_map_cor$snake_mu_rate, "_", big_map_cor$snake_mu_effect_sd,"_",big_map_cor$newt_mu_rate, "_", big_map_cor$newt_mu_effect_sd, "_", big_map_cor$rep)
big_map_cor$group <- paste0(big_map_cor$snake_mu_rate, "_", big_map_cor$snake_mu_effect_sd,"_",big_map_cor$newt_mu_rate, "_", big_map_cor$newt_mu_effect_sd)
big_map_cor$sim=LETTERS[factor(big_map_cor$group)]
big_map_cor$snake_newt_rep <- paste0("Snake_",big_map_cor$snake_mu_rate, "_", big_map_cor$snake_mu_effect_sd, "_Newt_",big_map_cor$newt_mu_rate, "_", big_map_cor$newt_mu_effect_sd, "_", big_map_cor$rep)


big_map_grid<-read.csv("~/Desktop/big_map/all_grid.txt" , header = TRUE)
filter_col=grepl( "X" , names( big_map_grid ))
big_map_grid= big_map_grid[, filter_col==FALSE]
big_map_grid_30<- read.csv("~/Desktop/big_map_30/all_grid.txt" , header = TRUE)
big_map_grid_30$rep=1
big_map_grid<-rbind(big_map_grid, big_map_grid_30)
big_map_grid$group <- paste0(big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd,"_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd)
big_map_grid$group_rep <- paste0(big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd,"_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd, "_", big_map_grid$rep)
big_map_grid$sim=LETTERS[factor(big_map_grid$group)]
big_map_grid$snake_newt_rep <- paste0("Snake_",big_map_grid$snake_mu_rate, "_", big_map_grid$snake_mu_effect_sd, "_Newt_",big_map_grid$newt_mu_rate, "_", big_map_grid$newt_mu_effect_sd, "_", big_map_grid$rep)



```


```{r, cor box set up}

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())


  return(plot)
}

hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  #unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  xlim(-1.1, 1.1)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())


  return(plot)
}

hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  #stat_bin(bins=30)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

suppressMessages(print(plot))

  return(plot)
}


var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  real_snewt_var = var(snewt$dif)
  var_cor_table=data.frame()

  
  for(i in 1:length(unique(file$snake_newt_rep))){
    pattern<-unique(file$snake_newt_rep)[i]
    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
    
    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
  }
 
  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
  
  plot <- ggplot(var_cor_table) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))


  return(plot)
}



cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
#file=big_map_tall
#cfile=big_map_cor 
 # pattern="Snake_1e-11_5_Newt_1e-10_0.5_0"
 
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
  
  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
    #ggtitle(title, subtitle = subt) +
    ylim(-1.1, 1.1)+
    #xlab(x_label_cor) + ylab(y_label)+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.margin=unit(c(-0.5,1,1,1), "cm"))
figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
  
  return(figure)
}


four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  geom_hline(yintercept=0, linetype="solid")+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())


  return(plot)
}

```


```{r, general file and graph making}

#the functions to make the params file and the summary and heatmap figures 

create_parm_file <- function(file, min_gen, max_gen){
params <- data_frame()

for(i in 1:length(unique(file$snake_newt_rep))){

  pattern=unique(file$snake_newt_rep)[i]
  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep ==pattern),]
 
  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
                           Newt_pop_size=mean(sumitup$Newt_pop_size),
                           Snake_pop_size=mean(sumitup$Snake_pop_size),
                           dif=mean(sumitup$dif),
                           snake_mu_rate=sumitup$snake_mu_rate[1],
                           newt_mu_rate=sumitup$newt_mu_rate[1],
                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
                           rep=sumitup$rep[1])
  
  
  params <- rbind(params, params_temp)
}

params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
params$snake_newt <- paste0(params$snake, "_", params$newt)
return(params)
}

GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, min_gen, max_gen)

my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

return(my_plot)
}
GA_summary_by_species <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, min_gen, max_gen)

my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=(get(x_line)), y=(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

return(my_plot)
}

build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
  params<-create_parm_file(file, min_gen, max_gen)
  
 my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))
 
 if(red_blue==FALSE){
  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
  }
 if(red_blue==TRUE){
  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
 }
 
  return(my_plot)
}

trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, rep){
 
  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
    facet_wrap(~sim)+
    geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())
  return(plot)
}

whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}


pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
  xlim((-1*themax)-5, themax+5)+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)
}

pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
  
  themin <- min(file$dif) 
  themax <- max(file$dif)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(dif), fill="aquamarine4")+
  xlim((-1*true_max)-1, true_max+1)+

  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}




two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
  
  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
  thedifmin <- min(file$dif) 
  thedifmax <- max(file$dif)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
dif <- ggplot(file) +
  
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
  
  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
  thedifmin <- min(file$dif) 
  thedifmax <- max(file$dif)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
  
dif <- ggplot(file) +
  
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      #strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      #panel.grid.major = element_blank(), 
                      #panel.grid.minor = element_blank(),
                      #panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file=big_map_tall
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
  
  thepopmin <- min(file$newt_deaths)
  thepopmax <- max(file$newt_deaths)
  thedifmin <- min(file$snake_deaths) 
  thedifmax <- max(file$snake_deaths)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
  
dif <- ggplot(file) +
  
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
  #scale_y_continuous(labels = scales::percent)+
  #xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  #geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      #strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      #panel.grid.major = element_blank(), 
                      #panel.grid.minor = element_blank(),
                      #panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

#two_hist_death_all_rep(big_map_tall, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)

grid_plot<- function(file_name, spegen, file, type, row_num, col_num){

GA1<-file[which(file$snake_newt_rep==file_name & file$generation==spegen),]
GA1_type = paste0("generation|", type)  

GA1_type = GA1[,grepl(GA1_type, names(GA1)) ]
GA1_type <- GA1_type[-1]

data_long_type_comp <- gather(GA1_type, condition, measurement, factor_key=TRUE)
data_long_type_comp[,c("species","type", "type2","location")]<- str_split_fixed(data_long_type_comp$condition, "_", 4)

data_long_type_comp$y_loc<- rep(sort(c(rep.int(row_num:1, 2)), decreasing = TRUE),5)

data_long_type_comp$x_loc<- sort(rep.int(1:col_num, row_num*2))
  
main_plot<-ggplot(data_long_type_comp)+
  
  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  ylim(0, 200)+
  xlim(0, 51)+
  theme_bw()+
  theme(legend.justification = "top")

if(type != "num_ind"){
main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance                                                          ")+
 scale_fill_viridis_c()
}
if(type == "num_ind"){
main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Newt/Snake Phenotype                                                         ")+
scale_fill_viridis_c(option = "plasma")
} 
  

snake<-data_long_type_comp[which(data_long_type_comp$species=="snake"),]
newt<-data_long_type_comp[which(data_long_type_comp$species=="newt"),]
newt$snake_value <- snake$measurement
print(cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs"))

newt$info <- "middle"
newt$info[newt$location %in% c(0, col_num-1, col_num*row_num-1-col_num, col_num*row_num-1)] <- "corner"

newt$info[newt$location %in% c(c(1:(col_num-2)), seq(col_num, (col_num*row_num-col_num-2), col_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-col_num):(col_num*row_num-2)))]   <- "edge"




extra_plot <- ggplot(newt)+
  ggtitle("Mean Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))



final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)
return(final_plot)}


```


### Phenotype differences 
```{r, graphing by gen}
trends_by_gen(big_map_tall, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)


```

```{r, average difference}
aggregate(big_map_tall[which(big_map_tall$generation>=100 & big_map_tall$generation<=50000),]$dif, list(big_map_tall[which(big_map_tall$generation>=100 & big_map_tall$generation<=50000),]$group), FUN=mean) 
```


## Connection between higher phenotype and population (5 sec) {.tabset}

### Phenotype differences
```{r, whale}
min_gen=100
max_gen=30000
rep=1

whale_gen(big_map_tall, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences 
```{r, popsize and pheno}

suppressMessages(print(two_hist(big_map_tall, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))


```

## {-}

### correlation
```{r, combo myplots}

ginmin = 100
ginmax = 30000

boxplot_cors_by_gen(big_map_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)


```


## Correlation across time {.tabset}

Next, we will examine three randomly chosen plots from both the 5 section and 7 section experiment. Time (in generations) in on the x-axis and both mean phenotype and phenotype spatial correlation in on the y-axis. Newt whole population mean phenotype is red, while snake mean phenotype is blue. The pink line is the phenotype spatial correlation.  


### Random 1 
```{r, GA1 cor and pheno}
GA1_pattern <- unique(big_map_tall$snake_newt_rep)

myrandomlist=sample.int(length(GA1_pattern), 3)


cor_trends_by_gen(big_map_tall, big_map_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=30000, pattern=GA1_pattern[myrandomlist[1]])

```

### Random 2 
```{r, random cor-pheno plot 2}

cor_trends_by_gen(big_map_tall, big_map_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

### Random 3 
```{r, random cor-pheno plot 3}

cor_trends_by_gen(big_map_tall, big_map_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

## {-}

## Summary {.tabset}

In the summary section, I try to come up with a way to show how different GA combinations can change the simulations results. In all of these plots snakes GA is represented by color and newt GA is represented by shape. There 16 color-shape combinations (with 4 repeats for trials). There are four sets of plots: 1) newt by snake population size, 2) phenotype difference by snake population size, 3) phenotype difference by snake GA, and 4) phenotype difference by newt GA. There are three figures in each set, taken at the begging, middle, and end time chunks. These are whole population calculations so the 5 section and 7 section data sets are not calculated differently. 


### Early-Sim Population Size Summary 

```{r, early plots summary}

min_gen=100
max_gen=30000
GA_summary(big_map_tall, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```



### Early Difference Summary
```{r, dif plots summary 1}

min_gen=100
max_gen=30000

GA_summary(big_map_tall, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```


### By Snake GA 
```{r, snakega plots summary 1}
min_gen=100
max_gen=30000
#

GA_summary_by_species(big_map_tall, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```



### By Newt GA 
```{r, newtga plots summary 1}
min_gen=100
max_gen=30000
#

GA_summary_by_species(big_map_tall, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

## {-}

## Heatmap {.tabset}


### Population Size 

```{r, early plots Heatmap}

min_gen=100
max_gen=30000
#heatmap
build_heatmap(big_map_tall, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```



### Phenotype 
```{r, early plots Heatmap pheno 1}
min_gen=100
max_gen=30000
build_heatmap(big_map_tall, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

## {-}


## What is up with the correlations




#### Mean 
```{r, cor grid high cor mean, fig.height=6, fig.width=8}

file=big_map_grid
file_name="Snake_1e-11_5_Newt_1e-10_0.5_0"
spegen=9501
type="mean"
row_num=200
col_num=50

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

```{r, cor grid high cor popsize, fig.height=6, fig.width=8}

file=big_map_grid
file_name="Snake_1e-11_5_Newt_1e-10_0.5_0"
spegen=9501
type="num_ind"
row_num=200
col_num=50
grid_plot(file_name, spegen, file, type, row_num, col_num)

```
