---
title: "1000 Graphs"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(viridis)
#setwd("~/Desktop/Proposal Old Drafts")
```

## This is a r file to show what the phenotypess are after 1000 generations
- A problem that I have been experiencing is that the phenotypes seem so go wild really quickly 
- This will be a graph that looks at the phenotypes of different simulations with a unique mutation rate and mutation effect size.

- Lets just visualize what the phenotypes are doing

## The Figure
Loop through the files and find the max and min of each of the species pheotypes
Then set up a graph with the max max
Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time

I made a mistake. I switched the mutation rates and the effect sizes

```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0
true_max = 0

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)

  if (max(file$Newt_max_Pheno) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno) }
  
  if (max(file$Snake_max_Pheno) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno) }
}
  print(newt_max_pheno)
  print(snake_max_pheno)
  
  if (newt_max_pheno > snake_max_pheno){
    true_max = newt_max_pheno }
  if ( snake_max_pheno > newt_max_pheno){
    true_max = snake_max_pheno }
  
```
```{r pressure, echo=FALSE}


files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  ylim(0, true_max)+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  theme_bw()

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)
 p <- p +
  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
  #Sys.sleep(2)

}

p 
```


## The Figure
Loop through the files and find the max and min of each of the species pheotypes
Then set up a graph with the max max
Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time

This is the correct one
```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0
true_max_2 = 0

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)
  #print(max(file$Newt_max_Pheno))
  #print(max(file$Snake_max_Pheno))
  if (max(file$Newt_max_Pheno) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno) }
  
  if (max(file$Snake_max_Pheno) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno) }
}

  print(newt_max_pheno)
  print(snake_max_pheno)
  
    if (newt_max_pheno > snake_max_pheno){
    true_max_2 = newt_max_pheno }
  if ( snake_max_pheno > newt_max_pheno){
    true_max_2 = snake_max_pheno }
```

```{r pressure, echo=FALSE}


files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  ylim(0, true_max_2)+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  theme_bw()

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)
 p <- p +
  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
  #Sys.sleep(2)

}

p 
```
## The Figure
Loop through the files and find the max and min of each of the species pheotypes
Then set up a graph with the max max
Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time 

This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked. 

```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0
true_max_3 = 0
max_difference = 0
min_difference = 0 

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

for (current_file in files){
  #print(current_file)
 
  file <- read.table(current_file, header = TRUE)
  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
  
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  #print(max(file$Newt_max_Pheno, na.rm = TRUE))
  #print(max(file$Snake_max_Pheno, na.rm = TRUE))
  if (as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) > newt_max_pheno){
    newt_max_pheno = as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) }
  
  if (as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) > snake_max_pheno){
    snake_max_pheno = as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) }
  
 if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference){
    min_difference = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }

  
  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference){
    max_difference = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }

      }

  print(newt_max_pheno)
  print(snake_max_pheno)
  print(min_difference)
  print(max_difference)
  if (newt_max_pheno > snake_max_pheno){
    true_max_3 = newt_max_pheno }
  if ( snake_max_pheno > newt_max_pheno){
    true_max_3 = snake_max_pheno }
```
some of these values are in quotes, why?

```{r pressure, echo=FALSE}


files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_3)+
  #scale_y_continuous(trans=log10_trans(), limits=c(0,true_max_3))+
  #scale_y_log10()+
  scale_y_log10(limits=c(0.001,true_max_3))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  theme_bw()

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  
 p <- p +
  geom_line(data=file, aes(y = as.numeric(Newt_mean_Pheno)), color = "darkred",na.rm=TRUE) + 
  geom_line(data=file, aes(y = as.numeric(Snake_mean_Pheno)), color="steelblue", linetype="twodash", na.rm=TRUE) 
  #Sys.sleep(2) na.rm=TRUE

}

p 
```


Some other things that might be goo to look at:

The difference between the average phenotypes



```{r pressure, echo=FALSE}


files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(min_difference, max_difference)+
  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
  #scale_y_log10()+
  scale_y_log10(limits=c(0.001, max_difference))+
  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
  theme_bw()

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  file <- file[complete.cases(file), ]
  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
  file$mean_dif[file$mean_dif == 0] <- 0.01
  file$pos <- TRUE
  file$pos[file$mean_dif < 0] <- FALSE
  

 p <- p + geom_line(data=file, aes(x=gen, y=abs(mean_dif), color = pos), na.rm=TRUE)
  #Sys.sleep(2) na.rm=TRUE
 # color = "mediumseagreen"

}

p 
```
