---
title: "1000 Graphs"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(viridis)
#setwd("~/Desktop/Proposal Old Drafts")
```

## This is a r file to show what the phenotypess are after 1000 generations
- A problem that I have been experiencing is that the phenotypes seem so go wild really quickly 
- This will be a graph that looks at the phenotypes of different simulations with a unique mutation rate and mutation effect size.

- Lets just visualize what the phenotypes are doing

## The Figure
Loop through the files and find the max and min of each of the species pheotypes
Then set up a graph with the max max
Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time

```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

for (current_file in files){
  print(current_file)

  file <- read.table(current_file, header = TRUE)
  print(max(file$Newt_max_Pheno))
  print(max(file$Snake_max_Pheno))
  if (max(file$Newt_max_Pheno) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno) }
  
  if (max(file$Snake_max_Pheno) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno) }
}
```


```{r pressure, echo=FALSE}
ggplot()+
  geom_line(current_file, aes(gen, snake), color="blue")+
  geom_line(current_file, aes(gen, snake), color="red")+
  geom_point(size=3, color = "darkgreen")+
  ggtitle("How the Phenotypes Change Through the Generations") + 
  xlab("Generation") + 
  ylab("Phenotype Level") +
  theme_bw()
```

