---
title: "Moving Together"
output: html_document
date: '2023-01-10'
---
```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE) 

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library(kableExtra)
library("reshape")
library(ggplot2)
library(ggpubr)
theme_set(theme_pubr())
library(stringr)
library(patchwork)
```

## Goal:

Start populations in the lower third of the simulation and let them move as they co-evolve. It is possible that as newts and snakes move into new territory they might create more spatial phenotype correlation. 

### Questions:

What does it mean to be correlated? Might this occur if I simulate some controlled movement?

## Background

I am running a coevolution experiment where newts and snakes interaction with each other over long periods of time. When they interact the newt or snake with the highest level of toxicity or resistance will survive. As newts and snake interact across space, they develop exaggerated traits that can become spatial correlated. My experiments examine when traits became exaggerated or correlated. 


## Experiment

I created a simulation study to observe the co-evolutionary outcome of the newt-snake interaction with different genetic architectures (GAs) in a spatial setting. I hypothesized that we would see an interaction (co-evolutionary arms race) between newt and snake phenotype under some GA combinations when newts and snakes were evolving over geographical space. Each GA is paired with another GA creating 16 combinations.

GA1 experiment values:

- 1e-8*(0.005)^2 = 2.5e-13
- 1e-9*(0.05)^2 = 2.5e-12
- 1e-10*(0.5)^2 = 2.5e-11
- 1e-11*(5.0)^2 = 2.5e-10



Each GA combination and trial has its own msprime simulation, but the msprime file is shared between the 5 section and 7 section slim runs.

### The data



```{bash, data file gathering}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=move_together
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_GA205_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_GA205_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_GA205_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")


#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```



```{r, data gathering}

snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)


move_together_lit<- read.csv("~/Desktop/move_together/all_lit.txt" , header = TRUE)

move_together_lit$group_rep <- paste0(move_together_lit$snake_mu_rate, "_", move_together_lit$snake_mu_effect_sd,"_",move_together_lit$newt_mu_rate, "_", move_together_lit$newt_mu_effect_sd, "_", move_together_lit$rep)

move_together_lit$group <- paste0(move_together_lit$snake_mu_rate, "_", move_together_lit$snake_mu_effect_sd,"_",move_together_lit$newt_mu_rate, "_", move_together_lit$newt_mu_effect_sd)

move_together_lit$sim=LETTERS[factor(move_together_lit$group)]
move_together_lit$dif <- move_together_lit$Snake_mean_Pheno-move_together_lit$Newt_mean_Pheno


move_together_cor<- read.csv("~/Desktop/move_together/all_cor.txt" , header = TRUE)
move_together_cor$group_rep <- paste0(move_together_cor$snake_mu_rate, "_", move_together_cor$snake_mu_effect_sd,"_",move_together_cor$newt_mu_rate, "_", move_together_cor$newt_mu_effect_sd, "_", move_together_cor$rep)
move_together_cor$group <- paste0(move_together_cor$snake_mu_rate, "_", move_together_cor$snake_mu_effect_sd,"_",move_together_cor$newt_mu_rate, "_", move_together_cor$newt_mu_effect_sd)
move_together_cor$sim=LETTERS[factor(move_together_cor$group)]

```



```{r, cor box set up}

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())


  return(plot)
}

hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  #unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  xlim(-1.1, 1.1)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())


  return(plot)
}

hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  #stat_bin(bins=30)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

suppressMessages(print(plot))

  return(plot)
}


var_cor <- function(file, cfile, title, subt, x_label, y_label, min_gen, max_gen){
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  real_snewt_var = var(snewt$dif)
  var_cor_table=data.frame()

  
  for(i in 1:length(unique(file$snake_newt_rep))){
    pattern<-unique(file$snake_newt_rep)[i]
    temp_file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
    temp_cor_file<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
    
    var_cor_table_temp<- data.frame("pattern"=pattern, "var"= var(temp_file$dif),"cor" = cor(temp_file$newt_toxin, temp_file$snake_res), "mean_corr" = mean(temp_cor_file$mean_newt_pheno_By_mean_snake_pheno))
    var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
  }
 
  var_cor_table_temp<- data.frame("pattern"="real", "var"= real_snewt_var, "cor" = real_snewt_cor, "mean_corr" = real_snewt_cor)
  var_cor_table <- rbind(var_cor_table, var_cor_table_temp)
  
  plot <- ggplot(var_cor_table) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(cor), color = pattern), shape=17, size=3)+
  geom_point(aes(x=as.numeric(var), y=as.numeric(mean_corr), color = pattern), size=3)+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))


  return(plot)
}



cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
#file=move_together_lit
#cfile=move_together_cor 
 # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
  
  cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col="CA"))+
    #ggtitle(title, subtitle = subt) +
    ylim(-1.1, 1.1)+
    #xlab(x_label_cor) + ylab(y_label)+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.margin=unit(c(-0.5,1,1,1), "cm"))
  
  file<-file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]
  cfile<-cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]
  
  if(nrow(cfile)>nrow(file)){
    toDelete <- seq(0, nrow(cfile), 2)
    cfile_short <-  cfile[-toDelete, ]
  }else{
    cfile_short <-  cfile
  }
  
  if(nrow(cfile_short)>nrow(file)){
      toDelete <- seq(0, nrow(cfile_short), 2)
      cfile_short <-  cfile_short[-toDelete, ]
    }
  figure <- ggarrange(plot, cor_plot + font("x.text", size = 10),heights = c(2, 1.5),ncol = 1, nrow = 2, align = "v")
    print(paste0("pattern ", pattern))
  print(paste0("Cor between average snake pheno and local cor ", cor(file$Snake_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average newt pheno and local cor ", cor(file$Newt_mean_Pheno, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between average dif pheno and local cor ", cor(file$dif, cfile_short$mean_newt_pheno_By_mean_snake_pheno)))
  print(paste0("Cor between newt pheno and snake ", cor(file$Newt_mean_Pheno, file$Snake_mean_Pheno)))
  return(figure)
}


four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  geom_hline(yintercept=0, linetype="solid")+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())


  return(plot)
}

```


```{r, general file and graph making}

#the functions to make the params file and the summary and heatmap figures 

create_parm_file <- function(file, min_gen, max_gen){
params <- data_frame()

for(i in 1:length(unique(file$snake_newt_rep))){

  pattern=unique(file$snake_newt_rep)[i]
  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep ==pattern),]
 
  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
                           Newt_pop_size=mean(sumitup$Newt_pop_size),
                           Snake_pop_size=mean(sumitup$Snake_pop_size),
                           dif=mean(sumitup$dif),
                           snake_mu_rate=sumitup$snake_mu_rate[1],
                           newt_mu_rate=sumitup$newt_mu_rate[1],
                           snake_mu_effect_sd=sumitup$snake_mu_effect_sd[1],
                           newt_mu_effect_sd=sumitup$newt_mu_effect_sd[1],
                           rep=sumitup$rep[1])
  
  
  params <- rbind(params, params_temp)
}

params$snake <- paste0(params$snake_mu_rate, "_",params$snake_mu_effect_sd)
params$newt <- paste0(params$newt_mu_rate, "_",params$newt_mu_effect_sd)
params$snake_newt <- paste0(params$snake, "_", params$newt)
return(params)
}

GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, min_gen, max_gen)

my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

return(my_plot)
}
GA_summary_by_species <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params<-create_parm_file(file, min_gen, max_gen)

my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=(get(x_line)), y=(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

return(my_plot)
}

build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
  params<-create_parm_file(file, min_gen, max_gen)
  
 my_plot <- ggplot(params, aes(newt, paste0(snake, "_", rep))) +    # Create heatmap with ggplot2
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))
 
 if(red_blue==FALSE){
  my_plot<- my_plot + scale_fill_viridis_c(name = fill_line_text) + theme(legend.text=element_text(angle = 45, hjust=1, size=10))
  }
 if(red_blue==TRUE){
  my_plot<- my_plot + scale_fill_gradient2(low = "red",mid = "beige", high = "blue", name = fill_line_text) + theme(legend.text=element_text(size=5))
 }
 
  return(my_plot)
}

trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, rep){
 
  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
    facet_wrap(~sim)+
    geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())
  return(plot)
}

whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}


pop_size_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
  themin <- min(file$Snake_pop_size-file$Newt_pop_size) 
  themax <- max(file$Snake_pop_size-file$Newt_pop_size)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(Snake_pop_size-Newt_pop_size), fill="darkolivegreen4")+
  xlim((-1*themax)-5, themax+5)+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)
}

pheno_dif_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
  
  themin <- min(file$dif) 
  themax <- max(file$dif)
  true_max <- max(abs(themin), abs(themax))
dif <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(dif), fill="aquamarine4")+
  xlim((-1*true_max)-1, true_max+1)+

  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}




two_hist <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]
  
  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
  thedifmin <- min(file$dif) 
  thedifmax <- max(file$dif)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
dif <- ggplot(file) +
  
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65)+
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65)+
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
  
  thepopmin <- min(file$Snake_pop_size-file$Newt_pop_size)/100 
  thepopmax <- max(file$Snake_pop_size-file$Newt_pop_size)/100
  thedifmin <- min(file$dif) 
  thedifmax <- max(file$dif)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
  
dif <- ggplot(file) +
  
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=dif, y=..count../data_points), fill="#8B008B",  alpha = 0.65, bins = 20)+ #purple
  geom_histogram(aes(x=(Snake_pop_size-Newt_pop_size)/100, y=..count../data_points), fill="#008B00",  alpha = 0.65, bins = 20)+ #green
  scale_y_continuous(labels = scales::percent)+
  xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      #strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      #panel.grid.major = element_blank(), 
                      #panel.grid.minor = element_blank(),
                      #panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file=move_together_lit
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  
  file<-file[ which(file$generation>=min_gen & file$generation<=max_gen),]
  
  thepopmin <- min(file$newt_deaths)
  thepopmax <- max(file$newt_deaths)
  thedifmin <- min(file$snake_deaths) 
  thedifmax <- max(file$snake_deaths)
  true_max <- max(abs(thepopmin), abs(thepopmax),abs(thedifmin), abs(thedifmax))

  data_points <- nrow(file[which(file$generation>=min_gen & file$generation<=max_gen  &  file$snake_GA==file$snake_GA[1] &  file$newt_GA==file$newt_GA[1]),])
  
dif <- ggplot(file) +
  
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=newt_deaths), fill="red",  alpha = 0.65, bins = 20)+
  geom_histogram(aes(x=snake_deaths), fill="blue",  alpha = 0.65, bins = 20)+
  #scale_y_continuous(labels = scales::percent)+
  #xlim((-1*true_max)-1, true_max+1)+
  # y=as.numeric(Snake_pop_size-Newt_pop_size), color = snake_GA, shape = factor(newt_GA)
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  #geom_vline(xintercept = 0)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      #strip.background = element_blank(), 
                      strip.text.x = element_blank(), 
                      #panel.grid.major = element_blank(), 
                      #panel.grid.minor = element_blank(),
                      #panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

}

#two_hist_death_all_rep(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)

grid_plot<- function(file_name, spegen, file, type, row_num, col_num){

file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd,"_",file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

GA1<-file[which(file$snake_newt_rep==file_name & file$generation==spegen),]
GA1_type = paste0("generation|", type)  

GA1_type = GA1[,grepl(GA1_type, names(GA1)) ]
GA1_type <- GA1_type[-1]

data_long_type_comp <- gather(GA1_type, condition, measurement, factor_key=TRUE)
data_long_type_comp[,c("species","type", "type2","location")]<- str_split_fixed(data_long_type_comp$condition, "_", 4)

data_long_type_comp$y_loc<- rep(sort(c(rep.int(row_num:1, 2)), decreasing = TRUE),col_num)

data_long_type_comp$x_loc<- sort(rep.int(1:col_num, row_num*2))
  
main_plot<-ggplot(data_long_type_comp)+
  
  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="snake"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 6, shape = 22, ) +
  geom_point(data = data_long_type_comp[which(data_long_type_comp$species=="newt"),], aes(x = x_loc, y = y_loc, fill = as.numeric(measurement)), size = 4, shape = 21, ) +
  scale_fill_viridis_c()+
  #ylim(0, row_num)+
  #xlim(0, col_num)+
  theme_bw()+
  theme(legend.justification = "top")

if(type != "num_ind"){
main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
 scale_fill_viridis_c()
}
if(type == "num_ind"){
main_plot<- main_plot + labs(title = paste0("Number of Individuals at Locations ", str_to_title(type)),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Newt/Snake PopSize")+
scale_fill_viridis_c(option = "plasma")
} 
  

snake<-data_long_type_comp[which(data_long_type_comp$species=="snake"),]
newt<-data_long_type_comp[which(data_long_type_comp$species=="newt"),]
newt$snake_value <- snake$measurement
print(cor(as.numeric(snake$measurement), as.numeric(newt$measurement), use="complete.obs"))

newt$info <- "middle"

#need to look into, coloring problem
newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-row_num, col_num*row_num-1)] <- "corner"

newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num), row_num),  c((col_num*row_num-row_num+1):(col_num*row_num-2)))]   <- "edge"


extra_plot <- ggplot(newt)+
  ggtitle("Mean Phenotype") +
  xlab("Newt") + ylab("Snake")+
  geom_point(aes(x = as.numeric(measurement), y = as.numeric(snake_value), color=info), size = 1 ) +
  theme_bw()+
   theme(text = element_text(size=10),title =element_text(size=8),
         legend.text = element_text(size = 8),
         legend.position ="bottom",
         legend.key.size = unit(0.1, "lines"),
         legend.title=element_blank())+
  guides(shape = guide_legend(override.aes = list(size = 1)),
         color = guide_legend(override.aes = list(size = 1)))



final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)
return(final_plot)}


```


## Mean Phenotype Whole Simulation {.tabset}




### Phenotype differences 
```{r, graphing by gen}
trends_by_gen(move_together_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)


#aggregate(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=50000),]$dif, list(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=50000),]$group_rep), FUN=mean) 

```

### Table of average Differences  

```{r, average difference}
aggregate(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=50000),]$dif, list(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=50000),]$group), FUN=mean) 
```


## {-}


## Connection between higher phenotype and population{.tabset}



### Phenotype differences 
```{r, whale}
min_gen=5000
max_gen=10000
rep=1

whale_gen(move_together_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences
```{r, popsize and pheno}

suppressMessages(print(two_hist(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

#suppressMessages(print(two_hist_all_rep(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))


```


## {-}



## Correlation

### cor
```{r, combo myplots}

ginmin = 10000
ginmax = 15000

boxplot_cors_by_gen(move_together_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)


#four_types_boxplot_cors_by_gen(move_together_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)


```





## Correlation Histograms{.tabset}



### Plot 1
```{r, GA1 cor by dif windows}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 2

```{r, GA1 cor by dif windows 2}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(move_together_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

## {-}

   

## Correlation across time {.tabset}



### Random 1  
```{r, GA1 cor and pheno}
GA1_pattern <- unique(paste0(move_together_lit$snake_mu_rate, "_", move_together_lit$snake_mu_effect_sd,"_",move_together_lit$newt_mu_rate, "_", move_together_lit$newt_mu_effect_sd, "_", move_together_lit$rep))

myrandomlist=sample.int(length(GA1_pattern), 3)

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(move_together_lit, move_together_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(move_together_lit, move_together_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

```

### Random 2  
```{r, random cor-pheno plot 2}

cor_trends_by_gen(move_together_lit, move_together_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

### Random 3  
```{r, random cor-pheno plot 3}

cor_trends_by_gen(move_together_lit, move_together_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

## {-}



## What happens over time (looking at the beginning, middle, and late part of my simulations) {.tabset}


### Pheno Beginning 

```{r, early plots}


min_gen=100
max_gen=5000


# for(i in 1:length(unique(move_together_lit$rep))){
#   myine<-whale_gen(move_together_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(move_together_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[1])
```

### Pheno Middle 

```{r, middle plots}


min_gen=25000
max_gen=30000


# for(i in 1:length(unique(move_together_lit$rep))){
#   myine<-whale_gen(move_together_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(move_together_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[1])
```

### Pheno End 

```{r, end plots}


min_gen=45000
max_gen=50000


# for(i in 1:length(unique(move_together_lit$rep))){
#   myine<-whale_gen(move_together_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(move_together_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[1])
```

### Dif Beginning 
```{r, early plots 1a}


min_gen=100
max_gen=5000


# for(i in 1:length(unique(move_together_lit$rep))){
#   myine<-two_hist(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[1] )

```

### Dif Middle 
```{r, early plots 2a}


min_gen=25000
max_gen=30000


# for(i in 1:length(unique(move_together_lit$rep))){
#   myine<-two_hist(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[1] )

```

### Dif End 
```{r, early plots 3a}


min_gen=45000
max_gen=50000


# for(i in 1:length(unique(move_together_lit$rep))){
#   myine<-two_hist(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(move_together_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(move_together_lit$rep)[1] )

```

## {-}



## Summary {.tabset}



### Early-Sim Population Size Summary 

```{r, early plots summary}

min_gen=100
max_gen=5000
GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Mid-Sim Population Size Summary
```{r, plots summary 2}
# summary

min_gen=25000
max_gen=30000

# summary
GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

### Late-Sim Population Size Summary
```{r, plots summary 3}
min_gen=45000
max_gen=50000

# summary
GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

```

### Early Difference Summary
```{r, dif plots summary 1}

min_gen=100
max_gen=5000

GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

### Mid Difference Summary
```{r, dif plots summary 2}
min_gen=25000
max_gen=30000


GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

```

### Late Difference Summary
```{r, dif plots summary 3}
min_gen=45000
max_gen=50000
GA_summary(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")


```

### By Snake GA (Early)
```{r, snakega plots summary 1}
min_gen=100
max_gen=5000
#

GA_summary_by_species(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Mid)
```{r, snakega plots summary 2}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Snake GA (Late)
```{r, snakega plots summary 3}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

```

### By Newt GA (Early)
```{r, newtga plots summary 1}
min_gen=100
max_gen=5000
#

GA_summary_by_species(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

### By Newt GA (Mid)
```{r, newtga plots summary 2}
min_gen=25000
max_gen=30000
#

GA_summary_by_species(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```


### By Newt GA (Late)
```{r, newtga plots summary 3}
min_gen=45000
max_gen=50000
#

GA_summary_by_species(move_together_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

```

## {-}


## Heatmap {.tabset}



### Population Size (Early) 

```{r, early plots Heatmap}

min_gen=100
max_gen=5000
#heatmap
build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)  
```{r, early plots Heatmap 2}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

```

### Population Size (Late) 
```{r, early plots Heatmap 3}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early) 
```{r, early plots Heatmap pheno 1}
min_gen=100
max_gen=5000
build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Mid) 
```{r, early plots Heatmap pheno 2}

min_gen=25000
max_gen=30000
#heatmap

build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

### Phenotype (Late) 
```{r, early plots Heatmap pheno 3}
min_gen=45000
max_gen=50000
#heatmap

build_heatmap(move_together_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

```

## {-}




```{r, red in grid files}
require(readr)
move_together_grid<- read.csv("~/Desktop/move_together/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
move_together_grid$group_rep <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd, "_", move_together_grid$rep)
move_together_grid$group <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd)
move_together_grid$sim=LETTERS[factor(move_together_grid$group)]
move_together_grid$grid_num = 5

```

## What is up with the correlations

## Early Simulation Correlation {.tabset}


### Mean 
```{r, cor grid high cor mean}

file=move_together_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Max 
```{r, cor grid high cor max}

file=move_together_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Min 
```{r, cor grid high cor min}

file=move_together_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize}

file=move_together_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name, spegen, file, type, row_num, col_num)

```

## {-}


```{r, red in grid files 2}
require(readr)
move_together_grid<- read.csv("~/Desktop/move_together/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
move_together_grid$group_rep <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd, "_", move_together_grid$rep)
move_together_grid$group <- paste0(move_together_grid$snake_mu_rate, "_", move_together_grid$snake_mu_effect_sd,"_",move_together_grid$newt_mu_rate, "_", move_together_grid$newt_mu_effect_sd)
move_together_grid$sim=LETTERS[factor(move_together_grid$group)]
move_together_grid$grid_num = 5

```




## Late Simulation Correlation {.tabset}


### Mean 
```{r, cor grid high cor mean late}

file=move_together_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Max 
```{r, cor grid high cor max late}

file=move_together_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Min 
```{r, cor grid high cor min late}

file=move_together_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late}

file=move_together_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name, spegen, file, type, row_num, col_num)

```

## {-}






